\bf Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-02-16 nips2015.tex
wip

\documentclass[12pt]{article}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{color}

%% \documentclass{article} % For LaTeX2e
%% \usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{qtree}
\usepackage{natbib}
\usepackage{graphicx}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09

@@

\author{
Elvis DOHMATOB
\\
Parietal team, Inria Saclay Ile-de-France\\
Saclay, France\\
\textit{email}: firstname.lastname@inria.fr}

@@

@@

\begin{abstract}
We present a simple primal-dual algorithm with a low cost per iteration for computing Nash $\epsilon$-equilibria in two-person zero-sum sequential games with imcomplete information and perfect-recall (like Texas Hold'em Poker), which converges after $\mathcal{O}(1/\epsilon)$ basic iterations (i.e iterations only involving basic operations like matvec, clipping, etc., and no calls to external first-order oracles, etc.). %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequen e-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010, chambolle2014ergodic}. It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the afore-mentioned games considered here since the strategy profiles (polytopes) of players are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to analytically compute
% (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
The core of our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point convex-convex problem which is amendable to the primal-dual scheme (i.e all proximal operators can be computed in closed-form). Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

\section{Introduction}
\label{sec:intro}
A game-theoretic aproach to playing games strategically optimally consists in computing Nash-equilibria (infact, approximations thereof) offline, and playing one's part of the equilibrium online. This technique is the driving-force behind solution concepts like CFR \cite{lanctot2009monte}, $\text{CFR}^{+}$, and other variants, which have recently found profound success in Poker: equilibria are computed offline (with tremendous computation resources, and the component optimal strategies are played on line by a bot, without any a posteriori computation). However, solving for equilibria remains a mathematical and computational challenge, especially in sequential games with imperfect information. This paper proposes an algorithm for solving for such equilibria approximately, in a sense which will be made clear shortly.

\subsection{Context}
The sequence-form for two-person zero-sum games was introduced in \cite{koller1992complexity}, and the theory was further developed in \cite{von1996efficient, vonequilibrium}, where it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
\begin{equation}
  \begin{aligned}
    & \underset{y,p}{\text{minimize}}
    & & p^Te_1 \\
    & \text{subject to}
    & & -Ay + E_1^Tp \geq 0,\\
    &&& E_2y = e_2,\\
    &&& y \ge 0
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

and the dual LCP problem
\begin{equation}
  \begin{aligned}
    & \underset{x,q}{\text{maximize}}
    & & -q^Te_2 \\
    & \text{subject to}
    & & -A^Tx + E_2^Tq \leq 0,\\
    &&& E_1x = e_1,\\
    &&& x \ge 0
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}

with \textit{duality gap} given by\footnote{The last inequality being due to \textit{weak duality}.}
\begin{equation}
  \mathcal{G}(p, q) := p^Te_1 - (-q^Te_2) = p^Te_1 + q^Te_2 \geq 0
  \label{eq:dgap}
\end{equation}

$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$. In this so-called \textit{sequence-form} representation (see section \ref{sec:rep} for details), the strategy profile of player $k$ is the polytope
\begin{equation}
  Q_k := \{z \ge 0\text{ }|\text{ }E_kz = e_k\} \subseteq \mathbb{R}^{n_k}
\label{eq:polytope}
\end{equation}

It was also shown (see Theorem 3.14 of \cite{vonequilibrium}) that a $(x, y)$ is a solution to the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff there exist vectors $p$ and $q$ such that
\begin{equation}
  \begin{split}
    E_1x = e_1,\text{ }x \geq 0,\hspace{1em} E_2y = e_2,\text{ }y \geq 0\\
    -Ay + E_1^Tp \geq 0,\hspace{1em}-A^Tx + E_2^Tq \leq 0
    \end{split}
\end{equation}

Moreover, in this case \textit{strong duality} holds and the value of the game equals $p^Te_1 = -q^Te_2$; thus the duality gap $\mathcal{G}(p, q)$ defined in \eqref{eq:dgap} vanishes.

@@

\begin{remark}  
It should be noted that even though problem \eqref{eq:primal_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
\end{remark}

% For the purpose of completeness we will cover the sequence-form representation in \ref{sec:rep}.

%% Though \textit{Nash equilibrium} has become a novel way for solving two-person zero-sum games, the problem of computing Nash equilibria for large-scale two-person zero-sum games is still largely unsolved. Even though this problem is, in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle.
%% We will be needing the following notation: %%  The reader should lookup any standard textbook
%% %% (for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions.
%% Viz,
%% \begin{itemize}
%% \item $\mathbb{R}^n$: $n$-dimensional real vector space;
%% \item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$n$ real matrices;
%% \item $0_{m,n}$: $m$-by-$n$ matrix of zeros;
%% \item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
%% \item $\mathbb{R}^n_+$: \quad $\{x \in \mathbb{R}^n|x = (x)_+\}$, the $n$-dimensional nonnegative orthant 
%% \item $i_C$: \quad indicator function of a convex set $C$;
%% % \item $\Pi_C$: \quad euclidean projection onto a convex set $C$;
%% \item $\|K\|_2$: \quad spectral norm of a matrix $K$
%% % \item $F^*$: the convex conjugate of a convex function $F$.
%% %% \item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
%% %% \item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
%% \end{itemize}

%% \section{Statement of the problem}
%% The Nash equilibrium problem for a two-person zero-sum sequential game with imcomplete information and perfect recall is a the saddle-point problem
%% \begin{equation}
%%   \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
%%   \label{eq:primal_pb}
%% \end{equation}

%% where player $k$'s \textit{strategy profile} $Q_k$ is the polytope
%% \begin{equation}
%%   Q_k := \{z \in \mathbb{R}^{n_k}| E_kz = e_k\text{ and } z_j \ge 0 \text{ }\forall j\}
%% \end{equation}
%% for %% some convex subset $C_k$ of a euclidean space $\mathbb{R}^{n_k}$, and 
%% some $l_k$-by-$n_k$ matrix $E_k$ and $l_k$-dimensional vector $e_k$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
%% $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
%% %% We will assume that the convex sets $C_k$ are simple enough so that the eucliean projections $\Pi_{C_k}$ can be cheaply computed.
%% Typically, $C_k = \mathbb{R}^{l_k}_+ := \{x \in \mathbb{R}^n|x_k \ge 0\}$, the \textit{the nonnegative orthant}, and encodes a nonnegativity constraint. %% in this case, $\Pi_{C_k}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
%% As usual, the ``minimax'' notation in problem \eqref{eq:primal_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
%% \begin{equation}
%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
%% \end{equation}
%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.

%% We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
%% \subsection{Simultaneous two-person zero-sum games}
%% \label{subsec:example_games}
%% Here, the Nash equilibrium problem takes the form \eqref{eq:primal_pb} with $l_k = 1$, $C_k = \mathbb{R}^{l_k}_+$, $E_k = 1_{1, n_k}$,
%%   and $e_k = 1$, so that $Q_k$ is simply the probabability $n_k$-simplex $\Delta_{n_k}$. Each point in $\Delta_{n_k}$ corresponds to a \textit{mixed-strategy} for player $j$,
%% and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_k}$).

%% \subsection{Two-person zero-sum sequential games with imcomplete information and perfect recall}
%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.

%% We recall that in the sequence-form representation of such games,  $E_k$ is a matrix whose
%% entries are $-1$, $0$, or $+1$, and $e_k := (1, 0, 0, ..., 0)$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
%% encode linear constraints player 1's (resp. player 2's)  ``admissible'' \textit{realization plans} $x$ (resp. $y$).

%% \subsection{Example of Nash equilibirum}
%% As an illustration, the pair $(x^*, y^*)$ given by
%% $x^* = [1, .478, .522, .174, .826]^T$ and
%% $y^* = [1, 1/2, 1/2]^T$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
%% $A = \left[\begin{array}{ccc}
%%   &   &  \\
%%   &   &  \\
%%   & 1 & -1\\
%%   & -2 & 4\\
%% 1 &   &  
%% \end{array}\right]$, $E_1 = \left[\begin{array}{ccccc}
%%   1 &   &   &   &  \\
%%   -1 & 1 & 1 &   &  \\
%%   -1 &   &   & 1 & 1
%% \end{array}\right]$,
%% $E_2 = \left[\begin{array}{ccc}
%%   1 &   &  \\
%%   -1 & 1 & 1
%% \end{array}\right]$, $e_1 = [1, 0, 0]^T$, and $e_2 = [1, 0]^T$.

\subsection{Statement of the problem}
Solving problem \eqref{eq:primal_pb} exactly is impossible in practice, and such a precision doesn't have any fundamental advantage. Instead, it is customary compute so-called Nash $\epsilon$-equlibria.

\begin{definition}(\textbf{Nash $\epsilon$-equilibria})
Given a margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} satisfying
\begin{equation}
  0 \le \mathcal{G}(p^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\end{definition}

The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations.
%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation. Then we state the Nash equilibrium problem for the sequence-form representation. Then in

\subsection{Outline of the article}
 Section \ref{sec:notation} exposes useful notions of convex optimization (proximal operators, convex conjugates, etc.) which will be crucial for the sequel. In section \ref{sec:related_work}, we give a brief overview of existing methods for computing Nash $\epsilon$-equilibria. In section \ref{sec:algo} we derive the proposed algorithm for producing a NAsh $\epsilon$-equilibrium and prove its $\mathcal{O}(1/\epsilon)$ convergence rate. Section \ref{sec:results} presents practical results obtained both on simulated matrix games and the Kuhn 3-card Poker \cite{kuhn}.

%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.

%% \section{The sequence-form representation}
%% \label{sec:rep}
%% In this section, we briefly recall the sequence-form representation of sequential games with imcomplete information and perfect recall. A complete overview of the subject can be found in the pioneering work \cite{von1996efficient}.

%% \subsection{The Game tree}
%% The game tree $\mathcal{T}$ is defined as follows. There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically. Nodes of the game tree $\mathcal{T}$ are identified with states of the game, and actions taken by players correspond to edges of $\mathcal{T}$.
%% The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops. %% The sequence-form is similar to the \textit{strategic-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
%% At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node. This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts. Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$. If each information set is a singleton, then the game reduces to a game complete information.

%% $a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
%% receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
%% The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
%% We will assume implicitly that each (non-chance) player is rational.

%% \subsection{Player sequences}
%% For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices from the root node, to $h$ (i.e to any node in $h$), ignoring the choices of the other players. \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
%% \begin{equation}
%% \mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
%% \end{equation}
%% Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
%% $\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

%% \subsection{Pure strategies, mixed strategies, realization plans}
%% Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$ (i.e the prescription of a move $c \in C_h$ from each information set $h \in \mathcal{I}_k$), and their \textit{mixed-strategies} are randomizations on these pure-strategies. A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts. The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.

%% The strategy profile of player $k$ is then the set of $n_k$-dimensional vectors $z$ satisfying
%% % Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
%% \begin{equation}
%%   z \geq 0,\hspace{1em}z(\emptyset) = 1,\hspace{1em}
%%     z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0, \hspace{1em} \forall h \in \mathcal{I}_k
%%   \label{eq:lin}
%% \end{equation}

%% These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
%% where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$, and so the polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}.

%% \subsection{Behavioral strategies}
%% Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioral-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
%% \begin{equation}
%%   \beta_k(h, c) := \begin{cases}
%%     z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
%%     0, &\mbox{Otherwise}.
%%   \end{cases}
%% \end{equation}

%% From this definition, it is clear that each behavioral-strategy is equivalent to a mixed-strategy.

%% \subsection{Payoff matrix}
%% The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
%% \begin{equation}
%%     A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \hspace{1em} \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
%%   \end{equation}

%% If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.

%% \subsection{In summary}
%% The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form and the LCP problems correspond to the Nash \textit{minimax} problem for such games. However, since we are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.

>>>>

\documentclass[12pt]{article}
\usepackage{amssymb}
\usepackage{color}

%% \documentclass{article} % For LaTeX2e
%% \usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage[sc, osf]{mathpazo}  %% for nice looking formulae, etc.
\usepackage{qtree}
\usepackage{natbib}
\usepackage{graphicx}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09

\usepackage[section]{placeins}

@@

\author{
Elvis DOHMATOB
\\
Parietal team, Inria Saclay Ile-de-France, Saclay, France\\
\textit{email}: elvis.dohmatob@inria.fr}

@@

\providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}

@@

\begin{abstract}
We present a simple primal-dual algorithm with a low cost per iteration for computing Nash $\epsilon$-equilibria in two-person zero-sum sequential games with imcomplete information and perfect recall (like Texas Hold'em Poker), which converges after $\mathcal{O}(1/\epsilon)$ basic iterations
(i.e iterations involving no
%o only involving basic operations like matvec, clipping, etc., and no
calls to external first-order oracles, etc.). %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequen e-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010, chambolle2014ergodic}. It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the aforementioned games considered here since the strategy profiles of players are polyhedra, so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to effectively compute % (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
The core of our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is amenable to the primal-dual scheme. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration. As an application, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

\keywords{sequential game; imcomplete information; perfect recall; sequence-form; Nash equilibrium; primal-dual algoithm; convex-optimization}

\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally consists in computing Nash-equilibria (infact, approximations thereof) offline, and playing one's part of the equilibrium online. This technique is the driving-force behind solution concepts like CFR (\textbf{TODO: add Z.'s ref first!!!}) \cite{lanctot2009monte}, $\text{CFR}^{+}$ \textbf{TODO: add ref!!!}, and other variants, which have recently had profound success in Poker. However, solving games for equilibria remains a mathematical and computational challenge, especially in sequential games with imperfect information. This paper proposes a simple and fast algorithm for solving for such equilibria approximately, in a sense which will be made clear shortly.

\subsection{Some notation}
Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq 0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The components of a vector $z \in \mathbb{R}^,$ will be denoted $z_0$, $z_1$, ..., $z_{n-1}$. The notation ``$z \ge 0$'' means that all the components of $z$ are nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in \mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with 0. For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$.  The operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp} function.

The \textit{spectral norm} of a matrix $K$, denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).

\subsection{The problem}
The sequence-form for two-person zero-sum games was introduced in \cite{koller1992complexity}, and the theory was further developed in \cite{von1996efficient, vonequilibrium}, where it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
\begin{equation}
  \begin{aligned}
    & \underset{y,p}{\text{minimize}}
    & & p_0 \\
    & \text{subject to}
    &&-Ay + E_1^Tp \geq 0,\\
    &&&\hspace{4em}E_2y = e_2,\\
    &&&\hspace{5em} y \ge 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

and the dual LCP problem
\begin{equation}
  \begin{aligned}
    & \underset{x,q}{\text{maximize}}
    && -q_0 \\
    & \text{subject to}
    && -A^Tx - E_2^Tq \leq 0,\\
    &&&\hspace{4.5em} E_1x = e_1,\\
    &&&\hspace{5.5em} x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$ and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$. In this so-called \textit{sequence-form} representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^n_+ |\text{ }E_kz = e_k\}
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and $e_2$. At a feasible point $(x, y, p, q)$, the \textit{duality gap} $\mathcal{G}(x, y, p, q)$ of primal-dual pair of problems is given by\footnote{The last inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(x, y, p, q) := p_0 - (-q_0) = p_0 + q_0
  \label{eq:dgap}
\end{equation}
Define the following closed convex sets
\begin{equation}
  \begin{aligned}
  \Sigma_1 &:= \{(y, p) \in \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\text{ }|\text{ } -Ay + E_1^Tp \ge 0, E_2y = e_2, y \ge 0\}\\
  \Sigma_2 &:= \{(x, q) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\text{ }|\text{ } -A^Tx - E_2^Tq \le 0, E_1x = e_1, x \ge 0\}
  \end{aligned}
  \label{eq:feasibility}
\end{equation}
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair $(x, y)$ is a solution to the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} if (and only if) there exist vectors $p$ and $q$ such that $(y, p) \in \Sigma_1$ and $(x, q) \in \Sigma_2$. Thus the problem of finding a Nash equilibrium is equivalent to the problem of finding a point in the cartesian product $\Sigma_1 \times \Sigma_2$. Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the duality gap $\mathcal{G}(x, y, p, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.

@@

\begin{remark}  
It should be noted that even though problem \eqref{eq:primal_pb} is in theory, amenable to classical tools like LCP (\textit{Linear Constraint Programming}), the class of games considered here (sequential games with imcomplete information) are exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
\end{remark}

Solving problem \eqref{eq:primal_pb} exactly is impossible in practice \textbf{Cite Koller!!!}, and such a precision doesn't have any fundamental advantage. Instead, it is customary compute so-called Nash $\epsilon$-equlibria.

\begin{definition}(\textbf{Nash $\epsilon$-equilibria})
Given a small margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} such that the duality gap at $(x^*, y^*, p^*, q^*)$ doesn't exceed $\epsilon$. That is,
\begin{equation}
  0 \le \mathcal{G}(x^*, y^*, p^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\end{definition}

\subsection{Precise statement of the problem}
The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations.
%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation. Then we state the Nash equilibrium problem for the sequence-form representation. Then in

\subsection{Outline of the article}
The next section features concepts from convex-analysis which will be used without further explanation. In section \ref{sec:related_work}, we give a brief overview of existing methods for computing Nash $\epsilon$-equilibria. In section \ref{sec:algo} we derive the proposed algorithm for producing a Nash $\epsilon$-equilibrium and prove its $\mathcal{O}(1/\epsilon)$ convergence rate. Section \ref{sec:results} presents practical results obtained both on simulated matrix games and the Kuhn 3-card Poker \cite{kuhn}.

\section{Useful convex-analysis}
\label{sec:notation}
We will need the following notations and concepts from convex-analysis in the sequel.
Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
\begin{equation}
  i_C(x) = \begin{cases}
    0, &\mbox{if } x \in C\\
    +\infty, &\mbox{otherwise}.
    \end{cases}
  \end{equation}
Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection} onto $C$, denoted $\Pi_C$, is the function
$\Pi: \mathbb{R}^n \mapsto C$ which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closest to $x$. Precisely,
\begin{equation}
  \Pi_C(x) := \underset{c \in C}{argimin}\text{ }\|c - x\|^2
\end{equation}
For example, the euclidean projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
% := \{x|\|x\| \le 1\}$
are $\Pi_{\mathbb{R}^n_+}(x) \equiv (x)_+$ and $\Pi_{\bar{\Delta}}(z) \equiv \dfrac{z}{max(\|z\|, 1)}$ respectively.

Let $f : \mathbb{R}^n \rightarrow [-\infty, +\infty]$ be a \textit{proper convex lower semi-continous function}
(\textit{p.c.l.s.c} for short). The \textit{convex conjugate} of $f$ is the function $f^*: \mathbb{R}^n \rightarrow [-\infty, +\infty]$ is defined by
\begin{equation}
  x \mapsto f^*(x) := \underset{z \in \mathbb{R}^n}{\text{max}}\text{ }z^Tx - f(z)
\end{equation}
